### 2016-07-12 HiggsCP/tex/paper.tex
higgs cp paper

\documentclass[preprintnumbers,nofootinbib,noshowpacs,eqsecnum,prd,superscriptaddress,letterpaper]{revtex4}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath,amssymb}
\usepackage{feynmp}
\usepackage{url}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{hyperref,color}
\renewcommand{\sfdefault}{phv}
\renewcommand{\baselinestretch}{1.2}

\DeclareGraphicsRule{*}{mps}{*}{}

\input{declare}

\usepackage{booktabs,siunitx}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\AtBeginDocument{
\heavyrulewidth=.08em
\lightrulewidth=.05em
\cmidrulewidth=.03em
\belowrulesep=.65ex
\belowbottomsep=0pt
\aboverulesep=.4ex
\abovetopsep=0pt
\cmidrulesep=\doublerulesep
\cmidrulekern=.5em
\defaultaddspace=.5em
}

\begin{document}

\title{Study of CP Violation in $h \rightarrow \tau^+\tau^-$ at Future
Lepton Collider}

\author{A.~Apyan}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}
\author{M.~Klute}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}
\affiliation{European Organization for Nuclear Research (CERN), Meyrin, CH}
\author{A.~Rios Tascon}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}

\begin{abstract} 
We evaluate the prospects for a measurement of the CP phase in $h\rightarrow\tau^+\tau^-$ at a future $e^+e^-$ collider. Previous studies have not considered detector effects and deemed them as negligible. We investigate how these effects affect the feasibility such a measurement. They are found to have important repercussions, and the accuracy of this measurement is severely limited.
\end{abstract}

\maketitle
\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
% Why is this an interesting question
% What are the options in studying CP violation in Higgs decays
% Why do we use Higgs to Tau Tau
% Why at e+e- collider
% What has been done on this channel before
% What are showing in this paper

Since the discovery of the Higgs boson in summer of 2012 by part of the CMS and ATLAS collaborations at CERN \cite{discovery}, it has been a topic of interest to check whether the discovered Higgs boson agrees in every aspect with the predictions made by the Standard Model (SM) of particle physics. Of particular importance, is the study of the couplings of the Higgs to other SM particles. The strengths of the couplings have been found to agree with predictions, as measured branching ratios agree with theory. A stronger test for the SM is the measurement of the CP phase in the couplings of the Higgs. It is predicted to have purely scalar couplings to all bosons and fermions. In fact, the purely pseudo-scalar coupling to electroweak gauge bosons has been excluded at 99.9\% confidence level at ATLAS \cite{atlas_cp1} and at 99.84\% (need to check this number) at CMS \cite{cms_cp}. The CP-mixing parameter $\tilde{d}$ was also constrained to the interval $[-0.11,0.05]$ at 68\% confidence level by ATLAS \cite{atlas_cp2}.\\

In this study we focus on a possible measurement of the CP phase in the coupling of the Higgs to taus. The most general form of the Lagrangian density from this coupling is
\begin{equation}
\mathcal{L}_{h-\tau\tau}=-\frac{y_\tau}{\sqrt{2}}h\bar{\tau}(\cos\Delta+i\gamma_5\sin\Delta)\tau,\label{eqn:lagrangian}
\end{equation}
where $y_\tau$ is a parameter fixing the strength of the coupling, and $\Delta$ is the mixing angle of scalar and pseudo-scalar contributions, with $\Delta=0$ corresponding to a purely scalar coupling and $\Delta=\pi/2$ to a purely pseudo-scalar one. Although current measurements disfavor a purely pseudo-scalar coupling, new physics in the TeV scale could result in a small pseudo-scalar contribution that is larger than in couplings to gauge bosons\cite{harnik}. In this study we focus on the $\Theta$-variable proposed by Harnik et al. in Ref.~\cite{harnik}. This variable makes use of the spin correlations of the taus in the $h\rightarrow\tau^+\tau^-$ decays to extract information about the CP phase of the coupling. It has been shown that this variable offers far greater discrimination power from other previously proposed variables, such as those in Refs.~\cite{worek,berge}. Thus, this variable lets us probe for a smaller pseudo-scalar component in the coupling. This method, however, is not optimal for use in a hadron collider. Due to the lack of precise information about the collision and the information loss due to neutrinos escaping the detector one must resort to using collinear approximations, which highly degrade the performance of this observable. Hence, we will focus on future lepton colliders such as the International Linear Collider (ILC) \cite{ilc} and FCC-ee (formerly known as TLEP), the proposed successor to the LHC \cite{fccee}.\\

In this paper we examine how this observable would work in a realistic detector environment considering detector resolution and inefficiencies not considered in previous studies. We first present how we generated our Monte Carlo samples and how we simulated detector effects. We then proceed to explain the event selection used and the statistical method used to determine the CP-phase value. Finally, we present our results and conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Event generation and simulation}
\label{sec:samples}
% Which tools do we use to generate and simulate

The generation of signal and background events and the calculation of leading order (LO) cross sections were done using MadGraph 5 \cite{madgraph}. The parton showering and hadronization was done using Pythia 8 \cite{pythia}. And the detector simulation was done using Delphes 3 \cite{delphes}. We used the Delphes card for the International Linear Detector (ILD), which is based on the expected performance presented in the Technical proposal for the ILD \cite{ilc}. Although the performance of the detector is not carefully modeled, this is used to investigate how an imperfect detector impacts the usefulness of the observable. In the previous study \cite{harnik}, the detector effects were deemed negligible and it was assumed that charged and neutral pions could easily be identified. Here we check whether this is the case.\\

We produce $Zh$ samples with a CP-phase of $n\pi/12$ with $n=0,1,2,\cdots,11$. We also consider the main backgrounds, which are $ZZ$, $Zll$, $jj$ and Drell-Yan.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Candidate selection}
\label{sec:selection}
% what is the event selection 
% explain how this was optimized

We begin by looking for jets with $p_T>20$ GeV reconstructed using the anti-$k_T$ algorithm \cite{cacciari} with a distance parameter of 0.4. For each jet we take the leading track lying within a distance of 0.2 of the jet axis. We require this track to have $p_T>0.5$ GeV and the remaining tracks in the jet to have in total $|\vec{p}_\text{total}|<5$ GeV. This ensures that the jet is consistent with a 1-prong decay from a $\tau$. We then pick the two leading photons in the jet. We require each of them to have $p_T>0.5$ GeV. The remaining photons in the jet are required to have a total of $|\vec{p}_\text{total}|<5$ GeV. This ensures that there was only one neutral pion in the tau decay. The jets that pass these requirement are taken as $\tau$-candidates. Events are then required to have two $\tau$-candidates with their corresponding selected tracks having opposite charges. If there are more than two candidates we take the ones with the highest track $p_T$.\\

Since we must also reconstruct the associated $Z$ boson, we require the events to have either two isolated leptons with $p_T>10$ GeV, or two additional jets with $p_T>20$ GeV. Since the reconstruction using leptons is far superior than using jets, we divide the events into those with leptonically and hadronically decaying $Z$'s. As we will show below, the observable of interest is highly sensitive on the reconstruction of the Higgs, and therefore of the $Z$, which renders the hadronic $Z$ events impractical. For this reason, here we only consider leptonic $Z$ events. As a last check, we require that the reconstructed mass of the $Z$ and its recoil mass satisfy $|m_{ll}-M_Z|<5$ GeV and $|m_\text{Recoil}-M_h|<5$ GeV.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statistical method}
\label{sec:method}
% what is the observable used
% what is the statistical method

The observable of interest is described in detail in Ref.~\cite{harnik}, here we recall the main features. An ``electric field" is defined as
\begin{equation}
\vec{E}_\pm=p^0_{\tau^\pm}\vec{k}_\pm-k^0_\pm\vec{p}_{\tau_\pm},\label{eqn:electricField}
\end{equation}
where $p^\mu_{\tau^\pm}=(p^0_{\tau^\pm},\vec{p}_{\tau^\pm})$ is the 4-momentum of $\tau^\pm$, and $k_\pm^\mu$ is given by
\begin{equation}
k^\mu_\pm\equiv y_\pm q^\mu_\pm+rp^\mu_{\nu^\pm},\qquad\text{ with }\qquad y_\pm\equiv\frac{2(p_{\pi^\pm}-p_{\pi^{0\pm}})\cdot p_{\tau^\pm}}{(p_{\pi^\pm}+p_{\pi^{0\pm}})\cdot p_{\tau^\pm}},\qquad r\equiv\frac{m_\rho^2-4m_\pi^2}{m_\tau^2+m_\rho^2}\approx 0.14,\label{eqn:thetaConst}
\end{equation}
and where $p^\mu_{\nu^\pm}$ is the 4-momentum of the neutrino from $\tau^\pm$. In the Higgs frame, for a boosted $\tau^\pm$ the magnitude of the component of this field that is perpendicular to the $\tau^\pm$ velocity is much greater than the magnitude of the parallel component. Hence, one can approximate this field as
\begin{equation}
\vec{E}_\pm \approx \frac{m_h}{2}\left[(y_\pm-r)\left.\vec{p}_{\pi^\pm}\right|_0-(y_\pm+r)\left.\vec{p}_{\pi^{0\pm}}\right|_0\right]^\perp,\label{eqn:electricApprox}
\end{equation}
where $\vec{p}_{\pi^\pm}$ is the 3-momentum of $\pi^\pm$, $\vec{p}_{\pi^{0\pm}}$ is the 3-momentum of the neutral pion from $\tau^\pm$, $|_0$ denotes evaluation in the Higgs frame, and $\perp$ denotes the perpendicular component to the $\tau^\pm$ velocity.\\

The $\Theta$-variable, which is the observable of interest, is thus defined as
\begin{equation}
\Theta=\text{sgn}\left[\vec{v}_{\tau^+}\cdot(\vec{E}_-\times\vec{E}_+)\right]\arccos\left(\frac{\vec{E}_+\cdot\vec{E}_-}{|\vec{E}_+||\vec{E}_-|}\right).\label{eqn:thetaVar}
\end{equation}

The distribution followed by this variable is given approximately by
\begin{equation}
P(\Theta)=A\cos(\Theta-2\Delta)+B,\label{eqn:thetaDistribution}
\end{equation}
for some constants $A$ and $B$. As we will show below, the overall shape of this distribution is unchanged by when considering detector effects and using the proposed event selection. However, the amplitude $A$ of the oscillation is reduced, which results in a decrease in the accuracy of the measurement. As it was mentioned before, this distribution is highly sensitive to the reconstruction of the Higgs momentum. In hadronic $Z$ events, the reconstruction is not ideal and the distribution of this variable becomes severely distorted.\\

To determine the uncertainty this measurement we first fitted the resulting distributions of the $\Theta$ variable with a function of the form \ref{eqn:thetaDistribution}. From them we averaged the values of $A$ and $B$ and interpolated to all other CP-phase angles $\Delta$. We then used a maximum likelihood method to estimate the uncertainty of the measurement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
% discuss the results
% (compare results with previous studies

The results from applying the proposed selection are shown in Table~\ref{tab:cutflow}. It can be seen that there is only a small portion of both signal and background left at the end. This is mainly due to the reconstruction of the associated $Z$ boson. The main theoretical advantage of using a lepton collider is that one can use this associated boson to reconstruct the 4-momentum of the Higgs. However, as we have mentioned before, the reconstruction from jets is not ideal and results in a severe distortion to the $\Theta$ variable distribution. Thus, one can only use the leptonic $Z$ events for this measurement. Ironically, it seems that it would instead be better to use collinear approximations to do this measurement, as with a hadron collider. In this case both signal and background yields would be much higher, but one could use additional cuts to obtain a better signal to background ratio. Furthermore, since backgrounds have been shown to have a flat $\theta$ distribution, one could still perform the measurement with high background levels.\\

\begin{table}[h]
\caption{\label{tab:cutflow}Cut-flow for $Zh$ events and main backgrounds using selection described in \ref{sec:selection} with a dataset of 1 ab$^{-1}$.}
\begin{tabularx}{0.8\textwidth}{c *{5}{Y}}
\toprule
\multirow{2}{*}{Requirement}
 & \multicolumn{1}{c}{Signal}  
 & \multicolumn{4}{c}{Backgrounds}\\
 \cmidrule(lr){2-2} \cmidrule(l){3-6}
 & $Zh\rightarrow Z\tau^+\tau^-$ & $ZZ$ & $Zll$\footnotemark[1] & $jj$ & Drell-Yan\\
\midrule
None & 15033 & 1163000 & 1497000 & 10270000 & 2954000\\
Two $\tau$-candidates & 775 & 8860 & 1142 & 7075 & 142688\\
Opposite $\tau$ charge & 657 & 5652 & 2078 & 4005 & 142496\\
Two leptons & 26 & 0 & 4.5 & 0 & 0\\
Mass cuts & 26 & 0 & 4.5 & 0 & 0\\
\bottomrule
\end{tabularx}
\footnotetext[1]{ZZ and Zh events are excluded here.}
\end{table}

The distribution of the $\Theta$ variable obtained with this selection is shown in Fig.~\ref{fig:thetaResult}. It can be seen that although the amplitude of the oscillation is reduced compared to the Monte Carlo truth, the overall shape of the distribution is unchanged. Hence, we can fit these distributions with functions of the form \ref{eqn:thetaDistribution} and estimate the uncertainty of the measurement as it was mentioned earlier.\\

\begin{figure}[hb]
\centering
\subfigure[Monte Carlo truth]{%
\includegraphics[width=.45\linewidth]{./fig/mc_theta.png}
\label{fig:mctheta}}
\quad
\subfigure[Reconstructed]{%
\includegraphics[width=.45\linewidth]{./fig/reco_theta.png}
\label{fig:recotheta}}
\caption{Comparison of $\Theta$ variable distribution between generated and reconstructed information for various values of the phase $\Delta$. Although the amplitude of the oscillation is decreased, the overall shape is preserved.}
\label{fig:thetaResult}
\end{figure}

From the maximum likelihood method we obtain an uncertainty on the measurement of $59^\circ$ for a dataset of 1 ab$^{-1}$. This is much worse than the $4.4^\circ$ uncertainty obtained by Ref.~\cite{harnik}. Thus, we see that detector effects play an important role in this measurement and cannot be neglected.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

We have shown that detector effects, which were neglected by previous studies, play an important role in this measurement. The main obstacle is to accurately reconstruct the $Z$ 4-momentum. This can only be done for leptonic $Z$ decays, which results in a very decreased signal yield culminating in a very limited accuracy of the measurement.

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

\bibitem{higgs}
 P.~W.~Higgs,
  %``Broken symmetries, massless particles and gauge fields,''
  Phys.\ Lett.\  {\bf 12}, 132 (1964);
  %%CITATION = PHLTA,12,132;%%
 P.~W.~Higgs,
  %``BROKEN SYMMETRIES AND THE MASSES OF GAUGE BOSONS,''
  Phys.\ Rev.\ Lett.\  {\bf 13}, 508 (1964);
  %%CITATION = PRLTA,13,508;%%
 F.~Englert and R.~Brout,
  %``BROKEN SYMMETRY AND THE MASS OF GAUGE VECTOR MESONS,''
  Phys.\ Rev.\ Lett.\  {\bf 13}, 321 (1964).
  %%CITATION = PRLTA,13,321;%%

\bibitem{discovery}
  G.~Aad {\it et al.} [ATLAS Collaboration],
  %% July 12 discovery paper
  Phys.\ Lett.\ B {\bf 716}, 1 (2012),
  %[arXiv:1207.7214 [hep-ex]]
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  %% July 12 discovery paper
  Phys.\ Lett.\ B {\bf 716}, 30 (2012).
  %[arXiv:1207.7235 [hep-ex]].

\bibitem{atlas_cp1}
  G.~Aad {\it et al.} [ATLAS Collaboration],
  Eur. Phys. J. {\bf C75} (2015) 476.
  %[arXiv:1506.05669v2]

\bibitem{cms_cp}
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  Phys. Rev. Lett. {\bf 110} (2013) 081803
  %[arXiv:1212.6639v2]

\bibitem{atlas_cp2}
  G.~Aad {\it et al.} [ATLAS Collaboration],
  	CERN-EP-2016-002.
  	%[arXiv:1602.04516v1]

\bibitem{harnik}
  R.~Harnik {\it et al.},
  Phys. Rev. D {\bf 88}, 076009 (2013)
  %[arXiv:1308.1094v1]

\bibitem{worek}
  M.~Worek,
  Acta Phys.Polon. {\bf B34} (2003) 5531-5538
  %[hep-ph/0310205]

\bibitem{berge}
  S.~Berge, W.~Bernreuther, and H.~Spiesberg,
  Phys. Lett. {\bf B727}, 488 (2013), 1308.2674
  %[arXiv:1308.1094v1]

\bibitem{ilc}
  Linear Collider Collaboration, ILC Technical Design Report, \url{http://www.linearcollider.org/ILC/Publications/Technical-Design-Report}

\bibitem{fccee}
  CERN, The FCC-ee design study, \url{http://tlep.web.cern.ch/}

\bibitem{madgraph}
  J.~Alwall {\it et al.},
  {\it JHEP} {\bf 07} (2014) 079.
  %[arXiv:1405.0301v2]

\bibitem{pythia}
  T.~Sjostrand, S.~Mrenna, and P.Z.~Skands,
  Comput. Phys. Commun. {\bf 178} (2008) 852–867.
  %[arXiv:0710.3820v1]

\bibitem{delphes}
  J.~de~Favereau {\it et al.} [DELPHES 3 collaboration],
  {\it JHEP} {\bf 02} (2014) 057.
  %[arXiv:1307.6346v3]

\bibitem{cacciari}
  M.~Cacciari, G.~Salam, G.~Soyez,
  {\it JHEP} {\bf 04}, 063 (2008), 0802.1189.
  %[arXiv:0802.1189]

\end{thebibliography}

\end{document}

### 2016-07-28 H_WW_Coupling/tex/paper.tex
Added H_WW_COUPLING folder

\documentclass[preprintnumbers,nofootinbib,noshowpacs,eqsecnum,prd,superscriptaddress,letterpaper]{revtex4}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath,amssymb}
% \usepackage{feynmp}
\usepackage{url}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{hyperref,color}
\renewcommand{\sfdefault}{phv}
\renewcommand{\baselinestretch}{1.2}

\DeclareGraphicsRule{*}{mps}{*}{}

\input{declare}

% \usepackage{booktabs,siunitx}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

% \AtBeginDocument{
% % \heavyrulewidth=.08em
% \lightrulewidth=.05em
% \cmidrulewidth=.03em
% \belowrulesep=.65ex
% \belowbottomsep=0pt
% \aboverulesep=.4ex
% \abovetopsep=0pt
% \cmidrulesep=\doublerulesep
% \cmidrulekern=.5em
% \defaultaddspace=.5em
% }

%Paper formatting based on Higgs CP study by Andres Rios - commented sections from this paper

\begin{document}

\title{Study of Higgs to WW Coupling Measurement Performance through $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ at Future
Circular Colider - Electron Positron}

\author{A.~Apyan}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}
\author{M.~Klute}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}
\affiliation{European Organization for Nuclear Research (CERN), Meyrin, CH}
\author{A.~Andriatis}
\affiliation{Massachusetts Institute of Technology, Cambrigde, USA}

\begin{abstract}
This investigation seeks to evaluate the potential performance capabilities of the measurment of Higgs to WW coupling at the FCCee - a future $e^+e^-$ collider. The signal process used in the investigation is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW Fusion, and considers various backgrounds. Unlike previous studies, this investigation closely evaluates the effect of detector performance on the coupling uncertainty. The model-independent uncertainty on Higgs to WW coupling is found to be !!! using an optimized detector.
\end{abstract}

\maketitle
\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

% Why e+ e- collider
% Why measure accurately
% Why Higgs WW
% Why nu nu b b
% What previous studies have been done
% Conclusions

The requirement on the precision of knowledge of Higgs Boson properties necessary to find new physics scales as $1/{\Lambda^2}$ \cite{TLEP}. For new physics at 1 TeV, per-cent sensitivity in Higgs couplings is ncecessary, while a per-mil sensitivity is necessary for multi-TeV new physics discoveries.

An $e^+e^-$ collider gives a clean and high-precision higgs factory useful for studying various higgs properties \cite{TLEP}.

The total width of the Higgs, and thus different higgs couplings, can be determined model-independently by studing the processes $e^+e^-\rig Z H $ and $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW fusion.

Previous studies have been done investigating Higgs Decays at the ILC \cite{Higgs ILC}, at TLEP \cite{TLEP} and at LEP3 using the CMS detector \cite{lep3}.

This study concludes that by constructing a detector specifically for the FCCee to investigate Higgs couplings, the uncertainty on the coupling of Higgs to WW can be determined to !!! percent and the uncertainty on the total higgs width, can be model-independently found to be !!!.

% In this study we focus on a possible measurement of the CP phase in the coupling of the Higgs to taus. The most general form of the Lagrangian density from this coupling is
% \begin{equation}
% \mathcal{L}_{h-\tau\tau}=-\frac{y_\tau}{\sqrt{2}}h\bar{\tau}(\cos\Delta+i\gamma_5\sin\Delta)\tau,\label{eqn:lagrangian}
% \end{equation}
% where $y_\tau$ is a parameter fixing the strength of the coupling, and $\Delta$ is the mixing angle of scalar and pseudo-scalar contributions, with $\Delta=0$ corresponding to a purely scalar coupling and $\Delta=\pi/2$ to a purely pseudo-scalar one. Although current measurements disfavor a purely pseudo-scalar coupling, new physics in the TeV scale could result in a small pseudo-scalar contribution that is larger than in couplings to gauge bosons\cite{harnik}. In this study we focus on the $\Theta$-variable proposed by Harnik et al. in Ref.~\cite{harnik}. This variable makes use of the spin correlations of the taus in the $h\rightarrow\tau^+\tau^-$ decays to extract information about the CP phase of the coupling. It has been shown that this variable offers far greater discrimination power from other previously proposed variables, such as those in Refs.~\cite{worek,berge}. Thus, this variable lets us probe for a smaller pseudo-scalar component in the coupling. This method, however, is not optimal for use in a hadron collider. Due to the lack of precise information about the collision and the information loss due to neutrinos escaping the detector one must resort to using collinear approximations, which highly degrade the performance of this observable. Hence, we will focus on future lepton colliders such as the International Linear Collider (ILC) \cite{ilc} and FCC-ee (formerly known as TLEP), the proposed successor to the LHC \cite{fccee}.\\

% In this paper we examine how this observable would work in a realistic detector environment considering detector resolution and inefficiencies not considered in previous studies. We first present how we generated our Monte Carlo samples and how we simulated detector effects. We then proceed to explain the event selection used and the statistical method used to determine the CP-phase value. Finally, we present our results and conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Event generation and simulation}
\label{sec:samples}
% Which tools do we use to generate and simulate

The generation of signal and background events was performed through Whizard \cite{whizard} which is a next-to-leading order tool and includes initial state radiation. Parton showering and hadronization was done using Pythia 8 \cite{pythia}. Detector simulation was done using Delphes \cite{delphes}. A card was made to simulate an optimal detector for Higgs precision studies at the FCCee.

The signal event produced is $\nu\bar{\nu}b\bar{b}$ through WW Fusion. The background events considered are $\nu\bar{\nu}b\bar{b}$ through ZH, $\nu\bar{\nu}c\bar{c}$, $\nu\bar{\nu}q\bar{q} (q\neq b,c)$, $q\bar{q}l^+l^-$, $q\bar{q}l^-\nu$, $q\bar{q}q\bar{q}$, $q\bar{q}$, and $q\bar{q}\gamma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Candidate selection}
\label{sec:selection}
% what is the event selection 
% explain how this was optimized

To select the WW Fusion $\nu\bar{nu}b\bar{b}$ signal, first a sample is created which looks for two jets reconstruccted using the anti-$k_T$ algorithn wth a distance parameter of 1.5. The jets are b-tagged with an efficiency specified by !!!. Only events containing two jets which are both b-tagged are allowed. Events with isolated leptons are omitted.

Next, kinematic cuts are applied based on the distribution of various properties. The visible mass of the system is required to be between 110 and 140 GeV since the visible mass from the signal comes only from the Higgs. The visible PT of the system is required to be greater than 15 GeV. The visible PZ is required to be less than 90 GeV. The number of charged tracks in the two jets is required to be between 10 and 30. The acoplanarity angle greater than 0.1, lab angle between 1.5 and 3, and CosTheta of the leading jet less than 0.95 further eliminates backgrounds. The visible energy of the system and recoil mass of the di-jet system are not considered because the uncertainty in the cross section and branching ratio of the Higgs bb system is given by the shape fit of the recoil mass, since at 350 GeV the missing mass has a large separation between the ZH and WW Fusion processes.

% We begin by looking for jets with $p_T>20$ GeV reconstructed using the anti-$k_T$ algorithm \cite{cacciari} with a distance parameter of 0.4. For each jet we take the leading track lying within a distance of 0.2 of the jet axis. We require this track to have $p_T>0.5$ GeV and the remaining tracks in the jet to have in total $|\vec{p}_\text{total}|<5$ GeV. This ensures that the jet is consistent with a 1-prong decay from a $\tau$. We then pick the two leading photons in the jet. We require each of them to have $p_T>0.5$ GeV. The remaining photons in the jet are required to have a total of $|\vec{p}_\text{total}|<5$ GeV. This ensures that there was only one neutral pion in the tau decay. The jets that pass these requirement are taken as $\tau$-candidates. Events are then required to have two $\tau$-candidates with their corresponding selected tracks having opposite charges. If there are more than two candidates we take the ones with the highest track $p_T$.\\

% Since we must also reconstruct the associated $Z$ boson, we require the events to have either two isolated leptons with $p_T>10$ GeV, or two additional jets with $p_T>20$ GeV. Since the reconstruction using leptons is far superior than using jets, we divide the events into those with leptonically and hadronically decaying $Z$'s. As we will show below, the observable of interest is highly sensitive on the reconstruction of the Higgs, and therefore of the $Z$, which renders the hadronic $Z$ events impractical. For this reason, here we only consider leptonic $Z$ events. As a last check, we require that the reconstructed mass of the $Z$ and its recoil mass satisfy $|m_{ll}-M_Z|<5$ GeV and $|m_\text{Recoil}-M_h|<5$ GeV.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statistical method}
\label{sec:method}
% what is the observable used
% what is the statistical method

The uncertainty in the quanitity of interest, $\sigma_{\nu\bar{\nu}H}$ x Br $(H \rig b\bar{b})$ is found using a Maximum Likelihood tool from HiggsAnalysis/CombinedLimit \cite{higgsanalysis}. This measurement is then combined with other measurements necessary to arrive at a total higgs width in a coupling tool \cite{couplingtool}.

The Maximum Likelihood tool allows the specification of systematic uncertainties. The unertainties used are a lognormal systematic uncertainty of 2.6\% on luminosity and an individual lognormal uncertainty of 1\% on each of the backgrounds and signal.

The analysis gives a total uncertainty of 2.29\% in $\sigma_{\nu\bar{\nu}H} x Br(H \rig b\bar{b})$. Compare this to an uncertainty of 10.5\% at 240 GeV and 0.66\% at 500 GeV given by the ILD paper \cite{ILD}.

The total higgs width was calculated to be !!! and the higgs WW coupling is calculated as !!!.

% The observable of interest is described in detail in Ref.~\cite{harnik}, here we recall the main features. An ``electric field" is defined as
% \begin{equation}
% \vec{E}_\pm=p^0_{\tau^\pm}\vec{k}_\pm-k^0_\pm\vec{p}_{\tau_\pm},\label{eqn:electricField}
% \end{equation}
% where $p^\mu_{\tau^\pm}=(p^0_{\tau^\pm},\vec{p}_{\tau^\pm})$ is the 4-momentum of $\tau^\pm$, and $k_\pm^\mu$ is given by
% \begin{equation}
% k^\mu_\pm\equiv y_\pm q^\mu_\pm+rp^\mu_{\nu^\pm},\qquad\text{ with }\qquad y_\pm\equiv\frac{2(p_{\pi^\pm}-p_{\pi^{0\pm}})\cdot p_{\tau^\pm}}{(p_{\pi^\pm}+p_{\pi^{0\pm}})\cdot p_{\tau^\pm}},\qquad r\equiv\frac{m_\rho^2-4m_\pi^2}{m_\tau^2+m_\rho^2}\approx 0.14,\label{eqn:thetaConst}
% \end{equation}
% and where $p^\mu_{\nu^\pm}$ is the 4-momentum of the neutrino from $\tau^\pm$. In the Higgs frame, for a boosted $\tau^\pm$ the magnitude of the component of this field that is perpendicular to the $\tau^\pm$ velocity is much greater than the magnitude of the parallel component. Hence, one can approximate this field as
% \begin{equation}
% \vec{E}_\pm \approx \frac{m_h}{2}\left[(y_\pm-r)\left.\vec{p}_{\pi^\pm}\right|_0-(y_\pm+r)\left.\vec{p}_{\pi^{0\pm}}\right|_0\right]^\perp,\label{eqn:electricApprox}
% \end{equation}
% where $\vec{p}_{\pi^\pm}$ is the 3-momentum of $\pi^\pm$, $\vec{p}_{\pi^{0\pm}}$ is the 3-momentum of the neutral pion from $\tau^\pm$, $|_0$ denotes evaluation in the Higgs frame, and $\perp$ denotes the perpendicular component to the $\tau^\pm$ velocity.\\

% The $\Theta$-variable, which is the observable of interest, is thus defined as
% \begin{equation}
% \Theta=\text{sgn}\left[\vec{v}_{\tau^+}\cdot(\vec{E}_-\times\vec{E}_+)\right]\arccos\left(\frac{\vec{E}_+\cdot\vec{E}_-}{|\vec{E}_+||\vec{E}_-|}\right).\label{eqn:thetaVar}
% \end{equation}

% The distribution followed by this variable is given approximately by
% \begin{equation}
% P(\Theta)=A\cos(\Theta-2\Delta)+B,\label{eqn:thetaDistribution}
% \end{equation}
% for some constants $A$ and $B$. As we will show below, the overall shape of this distribution is unchanged by when considering detector effects and using the proposed event selection. However, the amplitude $A$ of the oscillation is reduced, which results in a decrease in the accuracy of the measurement. As it was mentioned before, this distribution is highly sensitive to the reconstruction of the Higgs momentum. In hadronic $Z$ events, the reconstruction is not ideal and the distribution of this variable becomes severely distorted.\\

% To determine the uncertainty this measurement we first fitted the resulting distributions of the $\Theta$ variable with a function of the form \ref{eqn:thetaDistribution}. From them we averaged the values of $A$ and $B$ and interpolated to all other CP-phase angles $\Delta$. We then used a maximum likelihood method to estimate the uncertainty of the measurement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
% discuss the results
% (compare results with previous studies

The results found in this analysis suggests an improvement in the potential precision of Higgs to WW coupling measurements using an FCCee - specific detector, and improves the physics case for a circular electron positron precision higgs factory.

% The results from applying the proposed selection are shown in Table~\ref{tab:cutflow}. It can be seen that there is only a small portion of both signal and background left at the end. This is mainly due to the reconstruction of the associated $Z$ boson. The main theoretical advantage of using a lepton collider is that one can use this associated boson to reconstruct the 4-momentum of the Higgs. However, as we have mentioned before, the reconstruction from jets is not ideal and results in a severe distortion to the $\Theta$ variable distribution. Thus, one can only use the leptonic $Z$ events for this measurement. Ironically, it seems that it would instead be better to use collinear approximations to do this measurement, as with a hadron collider. In this case both signal and background yields would be much higher, but one could use additional cuts to obtain a better signal to background ratio. Furthermore, since backgrounds have been shown to have a flat $\theta$ distribution, one could still perform the measurement with high background levels.\\

% \begin{table}[h]
% \caption{\label{tab:cutflow}Cut-flow for $Zh$ events and main backgrounds using selection described in \ref{sec:selection} with a dataset of 1 ab$^{-1}$.}
% \begin{tabularx}{0.8\textwidth}{c *{5}{Y}}
% \toprule
% \multirow{2}{*}{Requirement}
%  & \multicolumn{1}{c}{Signal}  
%  & \multicolumn{4}{c}{Backgrounds}\\
%  \cmidrule(lr){2-2} \cmidrule(l){3-6}
%  & $Zh\rightarrow Z\tau^+\tau^-$ & $ZZ$ & $Zll$\footnotemark[1] & $jj$ & Drell-Yan\\
% \midrule
% None & 15033 & 1163000 & 1497000 & 10270000 & 2954000\\
% Two $\tau$-candidates & 775 & 8860 & 1142 & 7075 & 142688\\
% Opposite $\tau$ charge & 657 & 5652 & 2078 & 4005 & 142496\\
% Two leptons & 26 & 0 & 4.5 & 0 & 0\\
% Mass cuts & 26 & 0 & 4.5 & 0 & 0\\
% \bottomrule
% \end{tabularx}
% \footnotetext[1]{ZZ and Zh events are excluded here.}
% \end{table}

% The distribution of the $\Theta$ variable obtained with this selection is shown in Fig.~\ref{fig:thetaResult}. It can be seen that although the amplitude of the oscillation is reduced compared to the Monte Carlo truth, the overall shape of the distribution is unchanged. Hence, we can fit these distributions with functions of the form \ref{eqn:thetaDistribution} and estimate the uncertainty of the measurement as it was mentioned earlier.\\

% \begin{figure}[hb]
% \centering
% \subfigure[Monte Carlo truth]{%
% \includegraphics[width=.45\linewidth]{./fig/mc_theta.png}
% \label{fig:mctheta}}
% \quad
% \subfigure[Reconstructed]{%
% \includegraphics[width=.45\linewidth]{./fig/reco_theta.png}
% \label{fig:recotheta}}
% \caption{Comparison of $\Theta$ variable distribution between generated and reconstructed information for various values of the phase $\Delta$. Although the amplitude of the oscillation is decreased, the overall shape is preserved.}
% \label{fig:thetaResult}
% \end{figure}

% From the maximum likelihood method we obtain an uncertainty on the measurement of $59^\circ$ for a dataset of 1 ab$^{-1}$. This is much worse than the $4.4^\circ$ uncertainty obtained by Ref.~\cite{harnik}. Thus, we see that detector effects play an important role in this measurement and cannot be neglected.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

This will be the conclusion.

% We have shown that detector effects, which were neglected by previous studies, play an important role in this measurement. The main obstacle is to accurately reconstruct the $Z$ 4-momentum. This can only be done for leptonic $Z$ decays, which results in a very decreased signal yield culminating in a very limited accuracy of the measurement.

\clearpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{thebibliography}{99}

% \bibitem{higgs}
%  P.~W.~Higgs,
%   %``Broken symmetries, massless particles and gauge fields,''
%   Phys.\ Lett.\  {\bf 12}, 132 (1964);
%   %%CITATION = PHLTA,12,132;%%
%  P.~W.~Higgs,
%   %``BROKEN SYMMETRIES AND THE MASSES OF GAUGE BOSONS,''
%   Phys.\ Rev.\ Lett.\  {\bf 13}, 508 (1964);
%   %%CITATION = PRLTA,13,508;%%
%  F.~Englert and R.~Brout,
%   %``BROKEN SYMMETRY AND THE MASS OF GAUGE VECTOR MESONS,''
%   Phys.\ Rev.\ Lett.\  {\bf 13}, 321 (1964).
%   %%CITATION = PRLTA,13,321;%%

% \bibitem{discovery}
%   G.~Aad {\it et al.} [ATLAS Collaboration],
%   %% July 12 discovery paper
%   Phys.\ Lett.\ B {\bf 716}, 1 (2012),
%   %[arXiv:1207.7214 [hep-ex]]
%   S.~Chatrchyan {\it et al.}  [CMS Collaboration],
%   %% July 12 discovery paper
%   Phys.\ Lett.\ B {\bf 716}, 30 (2012).
%   %[arXiv:1207.7235 [hep-ex]].

% \bibitem{atlas_cp1}
%   G.~Aad {\it et al.} [ATLAS Collaboration],
%   Eur. Phys. J. {\bf C75} (2015) 476.
%   %[arXiv:1506.05669v2]

% \bibitem{cms_cp}
%   S.~Chatrchyan {\it et al.}  [CMS Collaboration],
%   Phys. Rev. Lett. {\bf 110} (2013) 081803
%   %[arXiv:1212.6639v2]

% \bibitem{atlas_cp2}
%   G.~Aad {\it et al.} [ATLAS Collaboration],
%   	CERN-EP-2016-002.
%   	%[arXiv:1602.04516v1]

% \bibitem{harnik}
%   R.~Harnik {\it et al.},
%   Phys. Rev. D {\bf 88}, 076009 (2013)
%   %[arXiv:1308.1094v1]

% \bibitem{worek}
%   M.~Worek,
%   Acta Phys.Polon. {\bf B34} (2003) 5531-5538
%   %[hep-ph/0310205]

% \bibitem{berge}
%   S.~Berge, W.~Bernreuther, and H.~Spiesberg,
%   Phys. Lett. {\bf B727}, 488 (2013), 1308.2674
%   %[arXiv:1308.1094v1]

% \bibitem{ilc}
%   Linear Collider Collaboration, ILC Technical Design Report, \url{http://www.linearcollider.org/ILC/Publications/Technical-Design-Report}

% \bibitem{fccee}
%   CERN, The FCC-ee design study, \url{http://tlep.web.cern.ch/}

% \bibitem{madgraph}
%   J.~Alwall {\it et al.},
%   {\it JHEP} {\bf 07} (2014) 079.
%   %[arXiv:1405.0301v2]

% \bibitem{pythia}
%   T.~Sjostrand, S.~Mrenna, and P.Z.~Skands,
%   Comput. Phys. Commun. {\bf 178} (2008) 852–867.
%   %[arXiv:0710.3820v1]

% \bibitem{delphes}
%   J.~de~Favereau {\it et al.} [DELPHES 3 collaboration],
%   {\it JHEP} {\bf 02} (2014) 057.
%   %[arXiv:1307.6346v3]

% \bibitem{cacciari}
%   M.~Cacciari, G.~Salam, G.~Soyez,
%   {\it JHEP} {\bf 04}, 063 (2008), 0802.1189.
%   %[arXiv:0802.1189]

% \end{thebibliography}

\end{document}

### 2016-07-28 H_WW_Coupling/tex/paper.tex
Thursday 1030 Updates

@@
 
-% In this study we focus on a possible measurement of the CP phase in the coupling of the Higgs to taus. The most general form of the Lagrangian density from this coupling is
-% \begin{equation}
-% \mathcal{L}_{h-\tau\tau}=-\frac{y_\tau}{\sqrt{2}}h\bar{\tau}(\cos\Delta+i\gamma_5\sin\Delta)\tau,\label{eqn:lagrangian}
-% \end{equation}
-% where $y_\tau$ is a parameter fixing the strength of the coupling, and $\Delta$ is the mixing angle of scalar and pseudo-scalar contributions, with $\Delta=0$ corresponding to a purely scalar coupling and $\Delta=\pi/2$ to a purely pseudo-scalar one.
-Although current measurements disfavor a purely pseudo-scalar coupling, new physics in the TeV scale could result in a small pseudo-scalar contribution that is larger than in couplings to gauge bosons\cite{harnik}.
-In this study we focus on the $\Theta$-variable proposed by Harnik et al.
-in Ref.~\cite{harnik}.
-This variable makes use of the spin correlations of the taus in the $h\rightarrow\tau^+\tau^-$ decays to extract information about the CP phase of the coupling.
-It has been shown that this variable offers far greater discrimination power from other previously proposed variables, such as those in Refs.~\cite{worek,berge}.
-Thus, this variable lets us probe for a smaller pseudo-scalar component in the coupling.
-This method, however, is not optimal for use in a hadron collider.
-Due to the lack of precise information about the collision and the information loss due to neutrinos escaping the detector one must resort to using collinear approximations, which highly degrade the performance of this observable.
-Hence, we will focus on future lepton colliders such as the International Linear Collider (ILC) \cite{ilc} and FCC-ee (formerly known as TLEP), the proposed successor to the LHC \cite{fccee}.\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Objects}
+\label{sec:samples}
+% What is used to detect the higgs signal
 
-% In this paper we examine how this observable would work in a realistic detector environment considering detector resolution and inefficiencies not considered in previous studies.
-We first present how we generated our Monte Carlo samples and how we simulated detector effects.
-We then proceed to explain the event selection used and the statistical method used to determine the CP-phase value.
-Finally, we present our results and conclusions.
+The signal process investigated is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW fusion
+
+% \includegraphics{WW Fusion Feynman Diagram}
+
+The visible decay products are two b-quarks, which hadronize into two jets which are the objects searched for by the detector. The mass of the b-quarks corresponds to the mass of the Higgs Boson
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Event generation and simulation}
+\section{MC Event generation and detector simulation}
 \label{sec:samples}
@@
 
-% We begin by looking for jets with $p_T>20$ GeV reconstructed using the anti-$k_T$ algorithm \cite{cacciari} with a distance parameter of 0.4.
-For each jet we take the leading track lying within a distance of 0.2 of the jet axis.
-We require this track to have $p_T>0.5$ GeV and the remaining tracks in the jet to have in total $|\vec{p}_\text{total}|<5$ GeV.
-This ensures that the jet is consistent with a 1-prong decay from a $\tau$.
-We then pick the two leading photons in the jet.
-We require each of them to have $p_T>0.5$ GeV.
-The remaining photons in the jet are required to have a total of $|\vec{p}_\text{total}|<5$ GeV.
-This ensures that there was only one neutral pion in the tau decay.
-The jets that pass these requirement are taken as $\tau$-candidates.
-Events are then required to have two $\tau$-candidates with their corresponding selected tracks having opposite charges.
-If there are more than two candidates we take the ones with the highest track $p_T$.\\
-
-% Since we must also reconstruct the associated $Z$ boson, we require the events to have either two isolated leptons with $p_T>10$ GeV, or two additional jets with $p_T>20$ GeV.
-Since the reconstruction using leptons is far superior than using jets, we divide the events into those with leptonically and hadronically decaying $Z$'s.
-As we will show below, the observable of interest is highly sensitive on the reconstruction of the Higgs, and therefore of the $Z$, which renders the hadronic $Z$ events impractical.
-For this reason, here we only consider leptonic $Z$ events.
-As a last check, we require that the reconstructed mass of the $Z$ and its recoil mass satisfy $|m_{ll}-M_Z|<5$ GeV and $|m_\text{Recoil}-M_h|<5$ GeV.\\
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% The observable of interest is described in detail in Ref.~\cite{harnik}, here we recall the main features. An ``electric field" is defined as
-% \begin{equation}
-% \vec{E}_\pm=p^0_{\tau^\pm}\vec{k}_\pm-k^0_\pm\vec{p}_{\tau_\pm},\label{eqn:electricField}
-% \end{equation}
-% where $p^\mu_{\tau^\pm}=(p^0_{\tau^\pm},\vec{p}_{\tau^\pm})$ is the 4-momentum of $\tau^\pm$, and $k_\pm^\mu$ is given by
-% \begin{equation}
-% k^\mu_\pm\equiv y_\pm q^\mu_\pm+rp^\mu_{\nu^\pm},\qquad\text{ with }\qquad y_\pm\equiv\frac{2(p_{\pi^\pm}-p_{\pi^{0\pm}})\cdot p_{\tau^\pm}}{(p_{\pi^\pm}+p_{\pi^{0\pm}})\cdot p_{\tau^\pm}},\qquad r\equiv\frac{m_\rho^2-4m_\pi^2}{m_\tau^2+m_\rho^2}\approx 0.14,\label{eqn:thetaConst}
-% \end{equation}
-% and where $p^\mu_{\nu^\pm}$ is the 4-momentum of the neutrino from $\tau^\pm$.
-In the Higgs frame, for a boosted $\tau^\pm$ the magnitude of the component of this field that is perpendicular to the $\tau^\pm$ velocity is much greater than the magnitude of the parallel component.
-Hence, one can approximate this field as
-% \begin{equation}
-% \vec{E}_\pm \approx \frac{m_h}{2}\left[(y_\pm-r)\left.\vec{p}_{\pi^\pm}\right|_0-(y_\pm+r)\left.\vec{p}_{\pi^{0\pm}}\right|_0\right]^\perp,\label{eqn:electricApprox}
-% \end{equation}
-% where $\vec{p}_{\pi^\pm}$ is the 3-momentum of $\pi^\pm$, $\vec{p}_{\pi^{0\pm}}$ is the 3-momentum of the neutral pion from $\tau^\pm$, $|_0$ denotes evaluation in the Higgs frame, and $\perp$ denotes the perpendicular component to the $\tau^\pm$ velocity.\\
-
-% The $\Theta$-variable, which is the observable of interest, is thus defined as
-% \begin{equation}
-% \Theta=\text{sgn}\left[\vec{v}_{\tau^+}\cdot(\vec{E}_-\times\vec{E}_+)\right]\arccos\left(\frac{\vec{E}_+\cdot\vec{E}_-}{|\vec{E}_+||\vec{E}_-|}\right).\label{eqn:thetaVar}
-% \end{equation}
-
-% The distribution followed by this variable is given approximately by
-% \begin{equation}
-% P(\Theta)=A\cos(\Theta-2\Delta)+B,\label{eqn:thetaDistribution}
-% \end{equation}
-% for some constants $A$ and $B$.
-As we will show below, the overall shape of this distribution is unchanged by when considering detector effects and using the proposed event selection.
-However, the amplitude $A$ of the oscillation is reduced, which results in a decrease in the accuracy of the measurement.
-As it was mentioned before, this distribution is highly sensitive to the reconstruction of the Higgs momentum.
-In hadronic $Z$ events, the reconstruction is not ideal and the distribution of this variable becomes severely distorted.\\
-
-% To determine the uncertainty this measurement we first fitted the resulting distributions of the $\Theta$ variable with a function of the form \ref{eqn:thetaDistribution}.
-From them we averaged the values of $A$ and $B$ and interpolated to all other CP-phase angles $\Delta$.
-We then used a maximum likelihood method to estimate the uncertainty of the measurement.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% The results from applying the proposed selection are shown in Table~\ref{tab:cutflow}.
-It can be seen that there is only a small portion of both signal and background left at the end.
-This is mainly due to the reconstruction of the associated $Z$ boson.
-The main theoretical advantage of using a lepton collider is that one can use this associated boson to reconstruct the 4-momentum of the Higgs.
-However, as we have mentioned before, the reconstruction from jets is not ideal and results in a severe distortion to the $\Theta$ variable distribution.
-Thus, one can only use the leptonic $Z$ events for this measurement.
-Ironically, it seems that it would instead be better to use collinear approximations to do this measurement, as with a hadron collider.
-In this case both signal and background yields would be much higher, but one could use additional cuts to obtain a better signal to background ratio.
-Furthermore, since backgrounds have been shown to have a flat $\theta$ distribution, one could still perform the measurement with high background levels.\\
-
-% \begin{table}[h]
-% \caption{\label{tab:cutflow}Cut-flow for $Zh$ events and main backgrounds using selection described in \ref{sec:selection} with a dataset of 1 ab$^{-1}$.}
-% \begin{tabularx}{0.8\textwidth}{c *{5}{Y}}
-% \toprule
-% \multirow{2}{*}{Requirement}
-%  & \multicolumn{1}{c}{Signal}  
-%  & \multicolumn{4}{c}{Backgrounds}\\
-%  \cmidrule(lr){2-2} \cmidrule(l){3-6}
-%  & $Zh\rightarrow Z\tau^+\tau^-$ & $ZZ$ & $Zll$\footnotemark[1] & $jj$ & Drell-Yan\\
-% \midrule
-% None & 15033 & 1163000 & 1497000 & 10270000 & 2954000\\
-% Two $\tau$-candidates & 775 & 8860 & 1142 & 7075 & 142688\\
-% Opposite $\tau$ charge & 657 & 5652 & 2078 & 4005 & 142496\\
-% Two leptons & 26 & 0 & 4.5 & 0 & 0\\
-% Mass cuts & 26 & 0 & 4.5 & 0 & 0\\
-% \bottomrule
-% \end{tabularx}
-% \footnotetext[1]{ZZ and Zh events are excluded here.}
-% \end{table}
-
-% The distribution of the $\Theta$ variable obtained with this selection is shown in Fig.~\ref{fig:thetaResult}.
-It can be seen that although the amplitude of the oscillation is reduced compared to the Monte Carlo truth, the overall shape of the distribution is unchanged.
-Hence, we can fit these distributions with functions of the form \ref{eqn:thetaDistribution} and estimate the uncertainty of the measurement as it was mentioned earlier.\\
-
-% \begin{figure}[hb]
-% \centering
-% \subfigure[Monte Carlo truth]{%
-% \includegraphics[width=.45\linewidth]{./fig/mc_theta.png}
-% \label{fig:mctheta}}
-% \quad
-% \subfigure[Reconstructed]{%
-% \includegraphics[width=.45\linewidth]{./fig/reco_theta.png}
-% \label{fig:recotheta}}
-% \caption{Comparison of $\Theta$ variable distribution between generated and reconstructed information for various values of the phase $\Delta$.
-Although the amplitude of the oscillation is decreased, the overall shape is preserved.}
-% \label{fig:thetaResult}
-% \end{figure}
-
-% From the maximum likelihood method we obtain an uncertainty on the measurement of $59^\circ$ for a dataset of 1 ab$^{-1}$.
-This is much worse than the $4.4^\circ$ uncertainty obtained by Ref.~\cite{harnik}.
-Thus, we see that detector effects play an important role in this measurement and cannot be neglected.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% We have shown that detector effects, which were neglected by previous studies, play an important role in this measurement.
-The main obstacle is to accurately reconstruct the $Z$ 4-momentum.
-This can only be done for leptonic $Z$ decays, which results in a very decreased signal yield culminating in a very limited accuracy of the measurement.
-
 \clearpage
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{thebibliography}{99}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{thebibliography}{99}
 
-% \bibitem{higgs}
-%  P.~W.~Higgs,
-%   %``Broken symmetries, massless particles and gauge fields,''
-%   Phys.\ Lett.\  {\bf 12}, 132 (1964);
-%   %%CITATION = PHLTA,12,132;%%
-%  P.~W.~Higgs,
-%   %``BROKEN SYMMETRIES AND THE MASSES OF GAUGE BOSONS,''
-%   Phys.\ Rev.\ Lett.\  {\bf 13}, 508 (1964);
-%   %%CITATION = PRLTA,13,508;%%
-%  F.~Englert and R.~Brout,
-%   %``BROKEN SYMMETRY AND THE MASS OF GAUGE VECTOR MESONS,''
-%   Phys.\ Rev.\ Lett.\  {\bf 13}, 321 (1964).
-%   %%CITATION = PRLTA,13,321;%%
+ \bibitem{fccee}
+   CERN, The FCC-ee design study, \url{http://tlep.web.cern.ch/}
 
-% \bibitem{discovery}
-%   G.~Aad {\it et al.} [ATLAS Collaboration],
-%   %% July 12 discovery paper
-%   Phys.\ Lett.\ B {\bf 716}, 1 (2012),
-%   %[arXiv:1207.7214 [hep-ex]]
-%   S.~Chatrchyan {\it et al.}  [CMS Collaboration],
-%   %% July 12 discovery paper
-%   Phys.\ Lett.\ B {\bf 716}, 30 (2012).
-%   %[arXiv:1207.7235 [hep-ex]].
+ \bibitem{madgraph}
+   J.~Alwall {\it et al.},
+   {\it JHEP} {\bf 07} (2014) 079.
+   %[arXiv:1405.0301v2]
 
-% \bibitem{atlas_cp1}
-%   G.~Aad {\it et al.} [ATLAS Collaboration],
-%   Eur. Phys. J. {\bf C75} (2015) 476.
-%   %[arXiv:1506.05669v2]
+ \bibitem{pythia}
+   T.~Sjostrand, S.~Mrenna, and P.Z.~Skands,
+   Comput. Phys. Commun. {\bf 178} (2008) 852–867.
+   %[arXiv:0710.3820v1]
 
-% \bibitem{cms_cp}
-%   S.~Chatrchyan {\it et al.}  [CMS Collaboration],
-%   Phys. Rev. Lett. {\bf 110} (2013) 081803
-%   %[arXiv:1212.6639v2]
+ \bibitem{delphes}
+   J.~de~Favereau {\it et al.} [DELPHES 3 collaboration],
+   {\it JHEP} {\bf 02} (2014) 057.
+   %[arXiv:1307.6346v3]
 
-% \bibitem{atlas_cp2}
-%   G.~Aad {\it et al.} [ATLAS Collaboration],
-%   	CERN-EP-2016-002.
-%   	%[arXiv:1602.04516v1]
-
-% \bibitem{harnik}
-%   R.~Harnik {\it et al.},
-%   Phys. Rev. D {\bf 88}, 076009 (2013)
-%   %[arXiv:1308.1094v1]
-
-% \bibitem{worek}
-%   M.~Worek,
-%   Acta Phys.Polon. {\bf B34} (2003) 5531-5538
-%   %[hep-ph/0310205]
-
-% \bibitem{berge}
-%   S.~Berge, W.~Bernreuther, and H.~Spiesberg,
-%   Phys. Lett. {\bf B727}, 488 (2013), 1308.2674
-%   %[arXiv:1308.1094v1]
-
-% \bibitem{ilc}
-%   Linear Collider Collaboration, ILC Technical Design Report, \url{http://www.linearcollider.org/ILC/Publications/Technical-Design-Report}
-
-% \bibitem{fccee}
-%   CERN, The FCC-ee design study, \url{http://tlep.web.cern.ch/}
-
-% \bibitem{madgraph}
-%   J.~Alwall {\it et al.},
-%   {\it JHEP} {\bf 07} (2014) 079.
-%   %[arXiv:1405.0301v2]
-
-% \bibitem{pythia}
-%   T.~Sjostrand, S.~Mrenna, and P.Z.~Skands,
-%   Comput. Phys. Commun. {\bf 178} (2008) 852–867.
-%   %[arXiv:0710.3820v1]
-
-% \bibitem{delphes}
-%   J.~de~Favereau {\it et al.} [DELPHES 3 collaboration],
-%   {\it JHEP} {\bf 02} (2014) 057.
-%   %[arXiv:1307.6346v3]
-
-% \bibitem{cacciari}
-%   M.~Cacciari, G.~Salam, G.~Soyez,
-%   {\it JHEP} {\bf 04}, 063 (2008), 0802.1189.
-%   %[arXiv:0802.1189]
-
-% \end{thebibliography}
+\end{thebibliography}
 

### 2016-08-02 H_WW_Coupling/tex/paper.tex
introduction revision and migration

@@
 \usepackage{amsmath,amssymb}
-% \usepackage{feynmp}
+\usepackage{feynmp}
 \usepackage{url}
@@
 
-% \usepackage{booktabs,siunitx}
+\usepackage{booktabs,siunitx}
 \usepackage{multirow}
@@
 
-% \AtBeginDocument{
-% % \heavyrulewidth=.08em
-% \lightrulewidth=.05em
-% \cmidrulewidth=.03em
-% \belowrulesep=.65ex
-% \belowbottomsep=0pt
-% \aboverulesep=.4ex
-% \abovetopsep=0pt
-% \cmidrulesep=\doublerulesep
-% \cmidrulekern=.5em
-% \defaultaddspace=.5em
-% }
+ \AtBeginDocument{
+ \heavyrulewidth=.08em
+ \lightrulewidth=.05em
+ \cmidrulewidth=.03em
+ \belowrulesep=.65ex
+ \belowbottomsep=0pt
+ \aboverulesep=.4ex
+ \abovetopsep=0pt
+ \cmidrulesep=\doublerulesep
+ \cmidrulekern=.5em
+ \defaultaddspace=.5em
+}
 
@@
 Unlike previous studies, this investigation closely evaluates the effect of detector performance on the coupling uncertainty.
-The model-independent uncertainty on Higgs to WW coupling is found to be !!!
-using an optimized detector.
+The uncertainty on the measurement of  $\sigma_{\nu\bar{\nu}H}$ x Br $(H \rig b\bar{b})$ is found to be 2.3\% at $\sqrt{s} = 350 \gev$ and 3.8\% at $\sqrt{s} = 240 \gev$, (compare to 0.6\% and 2.2\% in the TLEP paper) leading to a model-independent uncertainty on Higgs to WW coupling of 0.8\% and 1.1\%!
+respectively, and an uncertainty on the total higgs width of 1.1\% and 1.4\%, respectively (compare to 1.2\% and 2.4\% in the TLEP paper).
 \end{abstract}
@@
 
-The requirement on the precision of knowledge of Higgs Boson properties necessary to find new physics scales as $1/{\Lambda^2}$ \cite{TLEP}.
-For new physics at 1 TeV, per-cent sensitivity in Higgs couplings is ncecessary, while a per-mil sensitivity is necessary for multi-TeV new physics discoveries.
+To continue the search for physics beyond the standard model, precision knowledge of standard-model particles and their properties is required to measure deviations at higher energy scales.
+In investigating the Higgs boson, evidence for new physics at an energy scale of 1 TeV is expressed in deviations of the Higgs boson coupling to gauge bosons and fermions of up to 5\% relative to Standard Model predictions, and scales as $1/{\Lambda^2}$ \cite{tlep}.
+It is therefore necessary to measure Higgs boson couplings to per-cent accuracy or better to be sensitive to new physics at 1 TeV, and to per-mil accuracy or better to be sensitive to new  physics at multi-TeV.
 
-An $e^+e^-$ collider gives a clean and high-precision higgs factory useful for studying various higgs properties \cite{TLEP}.
+Among the possible machines proposed for a precision study of the standard model particles, the FCC-ee (Future Circular Collider electron-positron) stands out as the tool of choice.
+A circular $e^+e^-$ collider gives a high-luminosity higgs factory with a clean detection environment useful for studying various higgs properties as well as Z and W bosons and the top-quark \cite{TLEP}.
+
+Constraining the Higgs to W boson coupling ($g_\text{HWW}$) and the total Higgs boson width ($\Gamma_\text{tot}$) is a top priority.
+
+One path for this measurement is through studying the process $e^+e^-\rig\nu\bar{\nu} b\bar{b}$.
+This final state occurs through two processes, Higgs-strahlung (HZ) \ref{fig:hz_feyn} where the Z decays into a neutrino pair, and WW fusion \ref{fig:hz_feyn}.
+
+\begin{fmffile}{simple_labels}
+	\begin{fmfgraph}(40,25)
+		\fmfleft{i1,i2}
+		\fmfright{o1,o2}
+		\fmflabel{$e^-$}{i1}
+		\fmflabel{$e^+$}{i2}
+		\fmflabel{$h$}{o1}
+		\fmflabel{$z$}{o2}
+		\fmf{fermion}{i2,v1,i1}
+		\fmf{fermion}{o1,v2,o2}
+		\fmf{photon,label=$Z^*$}{v1,v2}
+	\end{fmfgraph}
+\end{fmffile}
 

### 2016-08-02 H_WW_Coupling/tex/paper.tex

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{hyperref,color}
+
 \renewcommand{\sfdefault}{phv}
@@
 \begin{abstract}
-This investigation seeks to evaluate the potential performance capabilities of the measurment of Higgs to WW coupling at the FCCee - a future $e^+e^-$ collider.
+This investigation seeks to evaluate the potential performance capabilities of the measurment of Higgs to WW coupling and the total Higgs decay width at the FCC-ee - a future $e^+e^-$ collider.
 The signal process used in the investigation is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW Fusion, and considers various backgrounds.
 Unlike previous studies, this investigation closely evaluates the effect of detector performance on the coupling uncertainty.
-The uncertainty on the measurement of  $\sigma_{\nu\bar{\nu}H}$ x Br $(H \rig b\bar{b})$ is found to be 2.3\% at $\sqrt{s} = 350 \gev$ and 3.8\% at $\sqrt{s} = 240 \gev$, (compare to 0.6\% and 2.2\% in the TLEP paper) leading to a model-independent uncertainty on Higgs to WW coupling of 0.8\% and 1.1\%!
-respectively, and an uncertainty on the total higgs width of 1.1\% and 1.4\%, respectively (compare to 1.2\% and 2.4\% in the TLEP paper).
+The uncertainty on the measurement of  $\sigma_{\nu\bar{\nu}H}$ x BR $(H \rig b\bar{b})$ is found to be 2.3\% at $\sqrt{s} = 350 \gev$ and 3.8\% at $\sqrt{s} = 240 \gev$, leading to a model-independent uncertainty on Higgs to WW coupling of 0.8\% and 1.1\% respectively, and an uncertainty on the total Higgs decay width of 1.1\% and 1.4\%, respectively.
 \end{abstract}
@@
 Among the possible machines proposed for a precision study of the standard model particles, the FCC-ee (Future Circular Collider electron-positron) stands out as the tool of choice.
-A circular $e^+e^-$ collider gives a high-luminosity higgs factory with a clean detection environment useful for studying various higgs properties as well as Z and W bosons and the top-quark \cite{TLEP}.
+A circular $e^+e^-$ collider provides a high-luminosity higgs factory with a clean detection environment useful for studying various higgs properties as well as Z and W bosons and the top-quark \cite{TLEP}.
 
@@
 One path for this measurement is through studying the process $e^+e^-\rig\nu\bar{\nu} b\bar{b}$.
-This final state occurs through two processes, Higgs-strahlung (HZ) \ref{fig:hz_feyn} where the Z decays into a neutrino pair, and WW fusion \ref{fig:hz_feyn}.
-
-\begin{fmffile}{simple_labels}
-	\begin{fmfgraph}(40,25)
+This final state occurs through two processes, Higgs-strahlung (HZ) (Figure \ref{fig:hz_feyn}) where the Z decays into a neutrino pair, and WW fusion (Figure \ref{fig:ww_feyn}).\\
+\begin{figure}[!htb]
+	\centering
+	\begin{minipage}{.5\textwidth}
+		\centering
+				\begin{fmffile}{zh}
+					\begin{fmfgraph*}(100,40)
 						\fmfleft{i1,i2}
 						\fmfright{o1,o2}
-		\fmflabel{$e^-$}{i1}
-		\fmflabel{$e^+$}{i2}
-		\fmflabel{$h$}{o1}
-		\fmflabel{$z$}{o2}
+						\fmflabel{$e^+$}{i1}
+						\fmflabel{$e^-$}{i2}
+						\fmflabel{$H$}{o2}
+						\fmflabel{$Z$}{o1}
 						\fmf{fermion}{i2,v1,i1}
-		\fmf{fermion}{o1,v2,o2}
-		\fmf{photon,label=$Z^*$}{v1,v2}
-	\end{fmfgraph}
+						\fmf{dashes}{v2,o2}
+						\fmf{boson}{v2,o1}
+						\fmf{boson,label=$Z^*$}{v1,v2}
+					\end{fmfgraph*}
 				\end{fmffile}
+		\caption{Higgs-strahlung}
+		\label{fig:hz_feyn}
+	\end{minipage}%
+	\begin{minipage}{0.5\textwidth}
+		\centering
+				\begin{fmffile}{ww}
+					\begin{fmfgraph*}(200,40)
+						\fmfleft{i1,i2}
+						\fmfright{o1,o2,o3}
+						\fmflabel{$e^+$}{i1}
+						\fmflabel{$e^-$}{i2}
+						\fmflabel{$\nu_{l}$}{o3}
+						\fmflabel{$H$}{o2}
+						\fmflabel{$\bar{\nu_{l}}$}{o1}
+						\fmf{fermion}{i2,v1,o3}
+						\fmf{fermion}{o1,v2,i1}
+						\fmf{boson}{v1,v3,v2}
+						\fmf{dashes}{v3,o2}
+						\fmf{boson,label=$W^+$}{v1,v3}
+						\fmf{boson,label=$W^-$}{v2,v3}
+					\end{fmfgraph*}
+				\end{fmffile}
+		\caption{WW Fusion}
+		\label{fig:ww_feyn}
+	\end{minipage}
+\end{figure}
 
-The total width of the Higgs, and thus different higgs couplings, can be determined model-independently by studing the processes $e^+e^-\rig Z H $ and $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW fusion.
+The measurement of $\sigma_{\nu\bar{\nu}H}$ x BR $(H \rig b\bar{b})$ contributes to the calculation of the total Higgs boson width, given by
+\begin{equation}
+	\Gamma_\text{tot} = \frac{\Gamma(\text{H}\rig\text{W W})}{\text{BR}(\text{H}\rig\text{W W})}
+\end{equation}
 
-Previous studies have been done investigating Higgs Decays at the ILC \cite{Higgs ILC}, at TLEP \cite{TLEP} and at LEP3 using the CMS detector \cite{lep3}.
+The uncertainty of the measurement of $\sigma_{\nu\bar{\nu}H}$ x BR $(H \rig b\bar{b})$, determined by fittting the WW Fusion profile to a Monte Carlo (MC) simulation of the $\nu\bar{\nu}b\bar{b}$ signal and backgrounds, can therefore be combined with previously published uncertainty calculations on Higgs branching ratios to determine the potential precision of the Higgs boson total width measurement at the FCC-ee.
 
-This study concludes that by constructing a detector specifically for the FCCee to investigate Higgs couplings, the uncertainty on the coupling of Higgs to WW can be determined to !!!
-percent and the uncertainty on the total higgs width, can be model-independently found to be !!!.
+Two center-of-mass energies are considered - $\sqrt{s} = 350 \gev$ and $\sqrt{s} = 240 \gev$.
+240 GeV is the center-of-mass energy proposed for the FCC as a Higgs factory, which balances the Higgs production cross section with the FCC-ee luminosity profile as a function of energy.
+While the Higgs cross-section peaks at 255 Gev, the FCC-ee luminosity decreases with increasing energy due to bremsstrahlung, leading to a maximum luminosity at $\sqrt{s} = 240 \gev$.
+It is proposed to run the FCC-ee at $\sqrt{s} = 240 \gev$ for five years, leading to a total integrated luminosity of 10 ab$^-1$ with four interaction points.
+The FCC-ee proposal also includes a five-year run at the $t\bar{t}$ threshold of $\sqrt{s} = 350 \gev$ with an integrated luminosity of 2.6 ab$^-1$.
+For this investigation, while large luminosity is preferable and decreases statistical uncertainty, the shape separation between the WW Fusion profile and its most similar background, ZH, increases as the available phase space of the missing mass increases.
+While the missing mass of the ZH background clusters around the Z boson mass of 91 GeV, the missing mass of the WW Fusion signal peaks at around $\sqrt{s}$ - m$_{H}$.
+A larger difference between the shape of the WW Fusion signal and its backgrounds leads to a lower uncertainty in the signal fit to the simulated data, thereby decreasing the uncertainty of the measurements.
+
+In the course of this study, the effects of detector performance on the precision of coupling measurements is investigated, and compared against detectors simulated in previous studies investigating Higgs decays at the ILC \cite{Higgs ILC}, at TLEP \cite{TLEP} and at LEP3 using the CMS detector \cite{lep3}.
 
@@
 
-The signal process investigated is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW fusion
-
-% \includegraphics{WW Fusion Feynman Diagram}
-
-The visible decay products are two b-quarks, which hadronize into two jets which are the objects searched for by the detector. The mass of the b-quarks corresponds to the mass of the Higgs Boson
+The signal process investigated is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW fusion.
+The visible decay products are two b-quarks, which hadronize into two jets of particles, and are the objects detected and reconstructed by the detector.
+Neutrinos escape the detector and are searched for through the profile of the missing four-momentum calculated from the two reconstructed jets.
 
@@
 
+The uncertainty on the measurement of  $\sigma_{\nu\bar{\nu}H}$ x Br $(H \rig b\bar{b})$ is found to be 2.3\% at $\sqrt{s} = 350 \gev$ and 3.8\% at $\sqrt{s} = 240 \gev$, (compare to 0.6\% and 2.2\% in the TLEP paper) leading to a model-independent uncertainty on Higgs to WW coupling of 0.8\% and 1.1\%!
+respectively, and an uncertainty on the total higgs width of 1.1\% and 1.4\%, respectively (compare to 1.2\% and 2.4\% in the TLEP paper).
+
 The results found in this analysis suggests an improvement in the potential precision of Higgs to WW coupling measurements using an FCCee - specific detector, and improves the physics case for a circular electron positron precision higgs factory.

### 2017-07-05 H_WW_Coupling/tex/paper.tex
Updates summary for Tuan

@@
 
+Jet reconstruction was first performed using the antikt algorithm included with the default Delphes distribution (\url{https://arxiv.org/pdf/0802.1189.pdf}).
+This algorithm defines a jet by the cluster of particles around a point with some cutoff distance.
+This is not optimized for the FCC, however, since our signal will contain only particles which come from one of the two jets and nothing else.
+Thus, it is better to define the two jets as a grouping of all the particles seen by the detector into exactly two jets.
+This is accomplished by the inclusive ee-kt algorithm which is included in Fastjet (\url{https://arxiv.org/pdf/1111.6097.pdf}).
+To do this, the Delphes installation was modified to interface a broader selection of algorithms.
+The modified code can be found in (\url{https://github.com/aandriat/MIT-FCCee/tree/master/jet_algs}) with FastJetFinder.cc being the crucial element, located in the Delphes/modules directory of your Delphes installation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Update: To more inclusively account for possible background processes, the background collection was changed to $e^+e^-\rig q\bar{q}$, $e^+e^-\rig W^{+}W{-}$, and $e^+e^-\rig ZZ$.
+However, I had trouble implementing this in Whizard becasue of on-shell constraints and double-counting if considering the final states of these processes.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To select the WW Fusion $\nu\bar{nu}b\bar{b}$ signal, first a sample is created which looks for two jets reconstruccted using the anti-$k_T$ algorithn wth a distance parameter of 1.5.
-The jets are b-tagged with an efficiency specified by !!!.
+To select the WW Fusion $\nu\bar{nu}b\bar{b}$ signal, first a sample is created which groups all detected particles into exactly two jets reconstruccted using the ee-$k_T$ algorithm.
+The jets are b-tagged with an efficiency specified by the Delphes deterctor simulation.
 Only events containing two jets which are both b-tagged are allowed.
@@
 Next, kinematic cuts are applied based on the distribution of various properties.
-The visible mass of the system is required to be between 110 and 140 GeV since the visible mass from the signal comes only from the Higgs.
-The visible PT of the system is required to be greater than 15 GeV.
-The visible PZ is required to be less than 90 GeV.
-The number of charged tracks in the two jets is required to be between 10 and 30.
-The acoplanarity angle greater than 0.1, lab angle between 1.5 and 3, and CosTheta of the leading jet less than 0.95 further eliminates backgrounds.
-The visible energy of the system and recoil mass of the di-jet system are not considered because the uncertainty in the cross section and branching ratio of the Higgs bb system is given by the shape fit of the recoil mass, since at 350 GeV the missing mass has a large separation between the ZH and WW Fusion processes.
+The optimal cuts were determined both by visual inspection of N-1 cut distributions, and through a BDT rectangular cut optimization tool in TMVVA.
+The visible mass of the system is required to be between 99 and 140 GeV since the visible mass from the signal comes only from the Higgs.
+The visible PT of the system is required to be less than 140 GeV.
+The visible PZ is required to be less than 130 GeV.
+The number of charged tracks in the two jets is required to be between 6 and 40.
+Lab angle between 1.5 and 3.
+Other parameters considered were the acoplanarity angle, and the CosTheta of the jet with respect to the beam axis, but were found to have negligible impact on the elimination of backgrounds.
+The visible energy of the system and recoil mass of the di-jet system are not considered for cuts because the uncertainty in the cross section and branching ratio of the Higgs bb system is given by the shape fit of the recoil mass, so the full distribution is left for the signal extraction.
+The implementation of cuts in the analysis code can be found in (\url{https://github.com/aandriat/MIT-FCCee/blob/master/vvbb_complete/install/treecutter_tree.C#L90}).
 
@@
 The unertainties used are a lognormal systematic uncertainty of 2.6\% on luminosity and an individual lognormal uncertainty of 1\% on each of the backgrounds and signal.
+As an additional feature, the ZH process can be considered as a second signal and is left with a floating normalization uncertainty, so that assumptions about the shape of the ZH distribution do not contribute to the measurement of the WW uncertainty.
+The setup for this measurement is shown in (\url{https://github.com/aandriat/MIT-FCCee/blob/master/vvbb_complete/install/xsection_tool.txt}).
 
